Cosmological Evidences of Dark Matter through the CMB

### 2019-02-28 paper/main.tex
restore old commit

\section{Conclusions}
The discovery of the CMB marked the beginning of a new era of cosmology.
On one hand the challenge of precise measurements of the CMB anisotropies accelerated the technological progress.
On the other hand the theoretical effort to build a cosmological model of the universe consistent with the observations lead to the discovery of new form of matter and energy.\\
We have seen that Dark Energy and the curvature do not affect the shape of the temperature power spectrum but they only shift the peaks.\\
The many ways that baryons show up in the power spectrum imply that the power spectrum has many independent checks on the baryon density of the universe \cite{huweb}.  
Therefore, the baryon density is a quantity that the CMB can measure accurately.\\
The dark matter plays a fundamental role in shaping the CMB power spectrum and it is the main constituent of matter in our universe.\\
The combined results from the phenomenology of the primordial plasma with the measurements of the temperature anisotropies and other astronomical observations produced the following estimates of the density parameters:
\begin{equation*}
    \Omega_{b} = 0.04917 
\qquad \Omega_{\Lambda 0} = 0.6844 \qquad \Omega_{dm} = 0.2647
\qquad \Omega_{r0} = 8.51 \times 10^{-5} 
\end{equation*}
with relative errors ranging from $0.8$ \% up to $1.6$ \% and $\Omega_{k0} = 0.001 \pm 0.002$.\\
It is evident from these parameters that we live in a spatially flat Universe mostly governed by Dark Energy.\\
In addition, dark matter is the dominant form of matter that constitutes the Universe.

>>>>

\section{Conclusions}
The discovery of the CMB marked the beginning of a new era of cosmology.
On one hand the challenge of precise measurements of the CMB anisotropies accelerated the technological progress.
On the other hand the theoretical effort to build a cosmological model of the universe consistent with the observations lead to the discovery of new form of matter and energy.\\
We have seen that Dark Energy and the curvature do not affect the shape of the temperature power spectrum but they only shift the peaks.\\
The many ways that baryons show up in the power spectrum imply that the power spectrum has many independent checks on the baryon density of the universe \cite{huweb}.  
Therefore, the baryon density is a quantity that the CMB can measure accurately.\\
The dark matter plays a fundamental role in shaping the CMB power spectrum and it is the main constituent of matter in our universe.\\
The combined results from the phenomenology of the primordial plasma with the measurements of the temperature anisotropies and other astronomical observations produced the following estimates of the density parameters:
\begin{equation*}
    \Omega_{b} = 0.04917 
\qquad \Omega_{\Lambda 0} = 0.6844 \qquad \Omega_{dm} = 0.2647
\qquad \Omega_{r0} = 8.51 \times 10^{-5} 
\end{equation*}
with relative errors ranging from $0.8$ \% up to $1.6$ \% and $\Omega_{k0} = 0.001 \pm 0.002$.\\
The density parameters are estimated with an astonishing precision and they reveal the true content of the Universe.
It is evident from these parameters that we live in a spatially flat Universe mostly governed by Dark Energy, which is the source of the accelerated expansion.\\
In addition, dark matter is the dominant form of matter that constitutes the Universe.
Dark matter plays a fundamental role in the early stages of the Universe through his gravitational interaction and it is the seed for the formation of structures in the Universe.
And the Cosmic Microwave Background gives one of the most compelling evidence of the existence of this new form of matter by using the best theory of gravity that we know: the General Theory of Relativity.
\pagebreak
